%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

%\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry} % Document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\name{Hongyuan Gao} % Your name
\address{\href{mailto://hongyuag@usc.edu}{hongyuag@usc.edu} \\ \href{https://github.com/hikoship}{github.com/hikoship} \\ \href{http://hgao.net}{hgao.net}} % Your address
\address{(213) 245-5576 \\ 2632 Ellendale Pl., Los Angeles, CA 90007} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	OBEJECTIVE
%----------------------------------------------------------------------------------------

% \begin{rSection}{Objective}
% CS graduate student seeking Software Engineering Intern position for Summer 2017.
% CS graduate student seeking Web Development Intern position for Summer 2017.
% \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

% \begin{rEducation}{University of Southern California}{August 2016 - May 2018 (expected)}{M.S. in Computer Science, GPA: 4.0 / 4.0}{Los Angeles, CA}
\begin{rEducation}{University of Southern California}{May 2018}{M.S. in Computer Science, GPA: 3.8 / 4.0}{Los Angeles, CA}
% \item Courses in progress: Analysis of Algorithms, Web Technologies.
\end{rEducation}

% \begin{rEducation}{Shanghai Jiao Tong University}{September 2012 - June 2016}{B.S. in Computer Science, GPA: 3.5 / 4.0}{Shanghai, China}
\begin{rEducation}{Shanghai Jiao Tong University}{June 2016}{B.S. in Computer Science, GPA: 3.5 / 4.0}{Shanghai, China}
% \item Core courses: Algorithms, Computer Architecture, Computer Networking, Data Structures, Database Systems, Operating Systems, Software Engineering.
% \item Core courses: Algorithms, Artificial Intelligence, Compilers, Computer Architecture, Computer Networking, Data Structures, Database Systems, Operating Systems, Software Engineering.
\end{rEducation}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\vspace{-0.3em} % Some space after the list of bullet points
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Python, C, C++, Java, JavaScript/Node.js, PHP\\
Web Frameworks & Bootstrap, React, AngularJS, Django, Tornado, Three.js\\
Tools & MySQL, SQLite, Redshift, S3, ESLint, Mocha, Git, Apache, Nginx, Vim
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Electronic Arts}{May 2017 - August 2017}{Software Engineering Intern}{Seattle, WA}
\item Developed a 3D web application to inspect gameplay events (eg. player tick, player death) on a 3D game terrain map using React and Three.js (a WebGL based 3D library).
\item Created a Node.js service to periodically query latest player data from internal database, transformed them to Three.js-friendly format and pushed them to Amazon S3.
\item Created a Node.js service to monitor new transformed data on S3 and import them to Amazon Redshift using COPY command with throughput of 60 thousand records / second.
\item Designed a Redshift database schema that can store hundreds of millions of gameplay event records.
\item Collaborated with team members to construct a set of powerful APIs to fetch games, maps and gameplay events.
\end{rSubsection}

\begin{rSubsection}{Embedded and Pervasive Computing Center of SJTU}{March 2015 - June 2016}{Research Assistant}{Shanghai, China}
\item Devised an efficient chunk-based cache algorithm for data deduplication in backup systems based on spacial locality; improved cache hit ratio by 5.2\%  and reduced I/O latency by 17.3\%.
\item Combined the algorithm with container technique and saved memory consumption by 50.7\%.
\item Won A-Class Bachelor's Thesis Award (top 10\%) and published a paper in IEEE ICPADS’16.
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	Project
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Forum Posts Crawler (JavaScript, Python)}{December 2015 - April 2016}{}{}
\item Utilized Beautiful Soup to parse HTML files of \href{http://1point3acres.com/bbs/forum.php}{1point3acres} (A forum for graduate school applicants) to JSON and visualized over 30,000 application results, which got about 1,000 visits from 17 countries within one month.
\item Developed a data filter based on AngularJS and a query API based on Tornado web framework.
\item Built a daemon program to manage and protect the crawler; deployed the daemon on DigitalOcean VPS.
\end{rSubsection}

\begin{rSubsection}{The US Congress Database: An Android App (Java, PHP)}{November 2016 - December 2016}{}{}
\item Visualized the US Congress data with a user-friendly interface based on Material Design language.
\item Constructed a powerful API to query thousands of legislators and bills data; hosted the API on AWS.
\item Designed 7 interfaces for users to search the data and save preferences.
\end{rSubsection}

% \begin{rSubsection}{Kickoff: A Soccer Statistics Website (JavsScript, PHP)}{May 2015 - June 2015}{}{}
% \item Established a large-scale database for thousands of UEFA soccer teams, players and matches.
% \item Developed a crawler to collect matches data from UEFA websites every day.
% \item Designed an interface for users to follow their favorite teams and give ratings to players after matches.
% \item Proposed an algorithm to select most valuable players according to their performances and ratings.
% \end{rSubsection}
%
\begin{rSubsection}{PDF Translation Platform (JavaScript, PHP)}{January 2015 - June 2015}{}{}
\item Collaborated with a team member and built an online platform for reading and translating public PDF files.
\item Created an intuitive front-end interface for translators to select sections they want to translate.
\item Devised an algorithm to bypass special characters and stored multiple versions of translations in database.
\end{rSubsection}

\begin{rSubsection}{Large-scale Patents Classifier (Python)}{March 2015 - May 2015}{}{Shanghai Jiao Tong University}
\item Developed a supervised learning model for classification using LIBLINEAR and LIBSVM library.
\item Led a 3-member group and constructed a multi-thread large-scale patents classifier with thread pool; achieved accuracy of 96.81\% by applying Min-Max Modular SVM.
\end{rSubsection}

\begin{rSubsection}{Netflix Movie Recommendation System (Python)}{January 2015 - March 2015}{}{Shanghai Jiao Tong University}
\item Predicted missing ratings of users based on given ratings in Netflix Prize Dataset.
\item Reduced the standard deviation of Netflix movie recommendation system to 0.90 (Top 5\% in the class) using multiple optimization algorithms such as stochastic gradient descent and collaborative filtering.
\end{rSubsection}

% \begin{rSubsection}{Visual Media and Data Management}{Sept. 2014 - Jan. 2015}{}{Shanghai Jiao Tong University}
% \item Led a team to accelerate video deblurring by using GPU parallel computing.
% \item Optimized Simple Linear Iteration Clustering (SLIC) algorithm and achieved higher accuracy in clustering pixels.
% %\item Proposed a faster method to calculate fuzzy kernel.
% \end{rSubsection}

\end{rSection}

% \begin{rSection}{Projects}

%\begin{rSubsection}{Podo Timer}{Jan. 2015 - Present}{}{}
%\item Wrote the Android app in Java and adopted Pomodoro technique for better time management.
%\item Provided various time period options for different types of tasks.
%\item Allowed users to record daily workload and evaluate their efficiency at work.
%\end{rSubsection}

% \begin{rSubsection}{Bluetooth Controller}{Sept. 2014 - Jan. 2015}{}{}
% \item Used an Android device to control a toy car through Bluetooth protocol.
% \item Implemented kinetic, gesture and voice user interfaces.
% \item Wrote a program to transfer live streaming video from a camera on the car to the Android device.
% \end{rSubsection}

% \end{rSection}

% %----------------------------------------------------------------------------------------
% %	SKILLS SECTION
% %----------------------------------------------------------------------------------------
%
% \begin{rSection}{Skills}
%
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Programming Languages & C, C++, Java (Android), Javascript, PHP, Python, SQL\\
% Tools \& Platforms & Apache, Git, Linux, Nginx, Vi (Vim)
% \end{tabular}
%
%
%----------------------------------------------------------------------------------------
%	Publication
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
H. Gao et al. An Efficient Cache Algorithm to Accelerate the I/O Processing of Data Deduplication in Storage Systems. In \textit{Proc. of the IEEE ICPADS’16}, 2016.
\end{rSection}

% \end{rSection}
%
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
